What's in a Name? Linear Temporal Logic Literally Represents Time Lines

### 2023-01-01 paper/main.tex
tikz

\usepackage{amsmath, amssymb, amsthm}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}{Lemma}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\newtheorem{example}{Example}[section]
\theoremstyle{remark}
\newtheorem{remark}{Remark}[section]

@@

\section{Theoretical Analyses}
\subsection{Correctness of Regex Translation}
\begin{lemma}
    % reduce_dfa does its input to output behaviour
    For any DFA $G$ and any state $v$ in $G$ that is neither a start state or a final state, \textbf{reduce\_dfa}$(G, v)$ preserves the regular language accepted by $G$
\end{lemma}
\begin{proof}
    Let $G'$ be the graph of $G$ post reduction by the application of \textbf{reduce\_dfa}$(G, v)$. We show that the trace of every path accepted by $G$ is also accepted by $G'$. Suppose a path accepted by $G$ does not pass through $v$, clearly this is true. Else, suppose it passes through $v$, since $v$ is an interior node, $v$ cannot be the first or last in the path. Thus, for every pass through $v$, let $u\neq v$ be the last node passed before entering $v$, and likewise $w$ be the first node after exiting $v$. We show that the regular language of sub-traces from $u$ to $w$ in $G$ (shown in \cref{fig:uvw-dfa}) is identical to that in $G'$.
    \begin{figure}[h!]
        \centering
        \includegraphics[scale=0.75]{img/uvw_dfa.pdf}
        \caption{$u$ to $w$ path in $G$}
        \label{fig:uvw-dfa}
    \end{figure}
    Suppose there is no loop at $v$, the path from $u$ to $w$ must simply be $u\xrightarrow{r_{uv}}v\xrightarrow{r_{vw}}w$, with the trace $r=r_{uv}r_{vw}$. If there is a loop edge $r_{vv}$, this edge can be traveled any number of times before exiting $v$, thus the regular expression is $r=r_{uv}r_{vv}^*r_{vw}$. This edge $u\xrightarrow{r}w$ is added in $G'$. Thus, for every path accepted by $G$, for every subpath entering and exiting $v$ from some $u$ to $w$, there exists a corresponding subpath from $u$ to $w$ in $G'$, and thus a corresponding path accepted by $G'$.
\end{proof}

@@

\noindent
\begin{tabular}{p{3.6in}|c|c}
  \hline
  Purpose & \# formulas & Source \\
  \hline
  Design space for NASA's AAC (Automated Airspace Concept) & 20,250 & \cite{GCMTR16} \\
  \hline
  Safety specifications for Boeing's AIR6110 wheel brake system & & \cite{BCFJKPRT15} \\
  \hline
  Requirements for model checking NASA's AAC high-level architecture & 6 & \cite{ZR14} \\
  \hline
  Real formulas collected from all publicly-available, pre-2011 case studies & 63 & \cite{RV11} \\
  \hline
\end{tabular}

>>>>

\usepackage{amsmath, amssymb, amsthm,tikz}
\usetikzlibrary{positioning,shapes,quotes}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}{Lemma}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\newtheorem{example}{Example}[section]
\theoremstyle{remark}
\newtheorem{remark}{Remark}[section]

@@

\section{Theoretical Analyses}
\subsection{Correctness of Regex Translation}
\begin{lemma}
    % reduce_dfa does its input to output behaviour
    For any DFA $G$ and any state $v$ in $G$ that is neither a start state or a final state, \textbf{reduce\_dfa}$(G, v)$ preserves the regular language accepted by $G$
\end{lemma}
\begin{proof}
    Let $G'$ be the graph of $G$ post reduction by the application of \textbf{reduce\_dfa}$(G, v)$. We show that the trace of every path accepted by $G$ is also accepted by $G'$. Suppose a path accepted by $G$ does not pass through $v$, clearly this is true. Else, suppose it passes through $v$, since $v$ is an interior node, $v$ cannot be the first or last in the path. Thus, for every pass through $v$, let $u\neq v$ be the last node passed before entering $v$, and likewise $w$ be the first node after exiting $v$. We show that the regular language of sub-traces from $u$ to $w$ in $G$ (shown in \cref{fig:uvw-dfa}) is identical to that in $G'$.
    \begin{figure}[h!]
        \centering
        \begin{tikzpicture}
	\node[draw, thick, shape=ellipse, style={minimum width=1.5cm}] (u) {$u$};
	\node[draw, thick, shape=ellipse, style={minimum width=1.5cm}] (v) [right=of u] {$v$};
	\node[draw, thick, shape=ellipse, style={minimum width=1.5cm}] (w) [right=of v] {$w$};
	\draw[thick] (u) edge["$r_{uv}$",-latex] (v) (v) edge["$r_{vv}$",-latex,loop above] (v) (v) edge["$r_{vw}$",-latex] (w); 
        \end{tikzpicture}
 %       \includegraphics[scale=0.75]{img/uvw_dfa.pdf}
        \caption{A path from $u$ to $w$ in $G$}
        \label{fig:uvw-dfa}
    \end{figure}
    Suppose there is no loop at $v$, the path from $u$ to $w$ must simply be $u\xrightarrow{r_{uv}}v\xrightarrow{r_{vw}}w$, with the trace $r=r_{uv}r_{vw}$. If there is a loop edge $r_{vv}$, this edge can be traveled any number of times before exiting $v$, thus the regular expression is $r=r_{uv}r_{vv}^*r_{vw}$. This edge $u\xrightarrow{r}w$ is added in $G'$. Thus, for every path accepted by $G$, for every subpath entering and exiting $v$ from some $u$ to $w$, there exists a corresponding subpath from $u$ to $w$ in $G'$, and thus a corresponding path accepted by $G'$.
\end{proof}

@@

\noindent
\begin{table}[h]
\begin{tabular}{p{3.6in}|c|c}
  \hline
  Purpose & \# formulas & Source \\
  \hline
  Design space for NASA's AAC (Automated Airspace Concept) & 20,250 & \cite{GCMTR16} \\
  \hline
  Safety specifications for Boeing's AIR6110 wheel brake system & & \cite{BCFJKPRT15} \\
  \hline
  Requirements for model checking NASA's AAC high-level architecture & 6 & \cite{ZR14} \\
  \hline
  Real formulas collected from all publicly-available, pre-2011 case studies & 63 & \cite{RV11} \\
  \hline
\end{tabular}
\end{table}
